# Site validation

## Auto site validation & use and assessment unit assignments
Performs an automated validation of site locations (e.g. appropriate sample location types, waterbody types, jurisdictions etc.). 
Also performs a spatial join between sites and beneficial use, assessment unit,  watershed managment unit, and UT jurisdiction polygon attributes to sites.
```{r, site-auto-validate, eval=F}
autoValidateWQPsites(
	sites_object=irdata$sites,
	master_site_file="02_site_validation/initial_master_site_file.xlsx",
	waterbody_type_file = "02_site_validation/waterbody_type_domain_table.csv",
	)
```

## Append external sites
JVL performed an initial site review to cleanup duplicated MLIDs and lat/longs.
Externally submitted sites that were found in the WQP were queried from WQP (some of these had duplicated MLIDs with the same name which were removed).

External sites that were not in the WQP were appended to the sites object, and the auto-validation was re-run including these sites and the externally submitted, requeried sites, using the JVL reviewed file as the master site file, to generate sites for review by other DWQ staff.
MonitoringLocationIdentifiers were assigned to two sites that were missing them (lower_web, nfork_ogden). 
Because all sites were reported in decimal degrees, horizontal datum was manually updated to WGS84 when left blank. 
Sites with blank site types were manually updated to River/Stream.


```{r, eval=F}
ext_sites_in_wqp1=read.csv(file='02_site_validation/external_sites/in_portal_external assessments mlids file 1.csv')
ext_sites_in_wqp2=read.csv(file='02_site_validation/external_sites/in_portal_external assessments mlids file 2.csv')
ext_sites=read.csv(file='02_site_validation/external_sites/not_in_portal_external assessments mlids file 1.csv')
ext_sites_all=plyr::rbind.fill(ext_sites_in_wqp1, ext_sites_in_wqp2, ext_sites)

dim(ext_sites_in_wqp1)
dim(ext_sites_all)

```
## Manual site validation

Sites were split out by WMU for manual site validation. The irTools::siteValApp() was used for reviewing sites. Following review by DWQ staff, all sites were appended back to a single file.

```{r, eval=F}

sites=as.data.frame(readxl::read_excel('02_site_validation/site-reviews-Jake-2019-08-02 2 ready for other reviews.xlsx', 'sites'))
reasons=as.data.frame(readxl::read_excel('02_site_validation/site-reviews-Jake-2019-08-02 2 ready for other reviews.xlsx', 'reasons'))

plyr::d_ply(sites, 'Mgmt_Unit', function(sdf) writexl::write_xlsx(list(sites=sdf, reasons=reasons), path=paste0('02_site_validation/manual_reviews/', sdf$Mgmt_Unit[1], ' sites.xlsx'), format_headers=F, col_names=T))

irTools::runSiteValApp()
```


### Incorporating manual reviews & accounting for AU edits
```{r, eval=F}
sites=read.csv("01_raw_data\\sites-2019-08-22.csv")
autoValidateWQPsites(
	sites_object=sites,
	master_site_file="P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/02_site_validation/master_site_file_08272019_norevsites.xlsx",
	waterbody_type_file = "02_site_validation/waterbody_type_domain_table.csv"
)
```

### Final round of manual reviews

### Final sites file:
P:\WQ\Integrated Report\IR_2020\2020-IR-assessments\assessment\02_site_validation\master_site_file_08292019_2020IR_final.xlsx
Pasted into translation workbook, also.














