# Initial data processing

## Data validation
Table-based validation.  
Functions to update & apply data validation tables, generate data with consistent nomenclature.  
1. Labs & activity types  
2. Activity media  
3. Parameter names & fractions  
4. Detection conditions  
5. Detection limit types  
6. Unit conversion factors  
7. Apply screening tables and subset to accepted data  
<br><br>

```{r, id-transwb, echo=FALSE}
translation_wb="P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/translations/ir_translation_workbook.xlsx"
```


### Read initial site review and reject data from auto-rejected sites before updating
```{r, eval=F}
sites_auto_val=as.data.frame(readxl::read_excel('P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/02_site_validation/site-reviews-Jake-2019-08-02 2 ready for other reviews.xlsx', 'sites'))
mlids=sites_auto_val$MonitoringLocationIdentifier[sites_auto_val$IR_FLAG!='REJECT']
update_table_data=irdata$merged_results[irdata$merged_results$MonitoringLocationIdentifier %in% mlids,]

```

### Update detection condition / limit name tables
```{r, update-detcondlim, eval=F}
updateDetCondLimTables(results=update_table_data, detquantlim=irdata$detquantlim, translation_wb=translation_wb,
						detConditionTable_startRow=3, detLimitTypeTable_startRow=3)
```

### Update lab/activity & media tables
```{r, labactmedia, eval=F}
updateLabActMediaTables(update_table_data, translation_wb=translation_wb, labNameActivityTable_startRow = 2)
```

### Update parameter translation tables
```{r, update-param-trans, eval=F}
updateParamTrans(data=update_table_data, detquantlim=irdata$detquantlim,  translation_wb=translation_wb, WQPParamCASID_startRow = 4)
```



## Apply screening tables
1. Sites
2. Activity media
3. Lab/activity
4. Parameter translation table

library(magrittr)
translation_wb='ir_translation_workbook_working.xlsx'
merged_results=irdata$merged_results %>%
	applyScreenTable(wb=translation_wb, sheetname="masterSiteTable", startRow=1, flag_col_name="IR_Site_FLAG", com_col_name="IR_Site_COMMENT") %>% 
	subset(IR_Site_FLAG=='ACCEPT') %>% 
	applyScreenTable(wb=translation_wb, sheetname="activityMediaNameTable", startRow=1, flag_col_name="IR_ActMedia_FLAG", com_col_name="IR_ActMedia_COMMENT") %>% 
	applyScreenTable(wb=translation_wb, sheetname="labNameActivityTable", startRow=3, flag_col_name="IR_LabAct_FLAG", com_col_name="IR_LabAct_COMMENT") %>% 
	applyScreenTable(wb=translation_wb, sheetname="detConditionTable", startRow=3, flag_col_name="IR_DetCond_FLAG", com_col_name="IR_DetCond_COMMENT")

rej_data=subset(merged_results, IR_Site_FLAG=='REJECT' | IR_ActMedia_FLAG=='REJECT' | IR_LabAct_FLAG=='REJECT' | IR_DetCond_FLAG=='REJECT')
acc_data=subset(merged_results, IR_Site_FLAG=='ACCEPT' & IR_ActMedia_FLAG=='ACCEPT' & IR_LabAct_FLAG=='ACCEPT' & IR_DetCond_FLAG=='ACCEPT')

acc_data=applyScreenTable(acc_data, wb=translation_wb, sheetname="paramTransTable", startRow=4, flag_col_name="IR_Parameter_FLAG", com_col_name="IR_Parameter_COMMENT")



	
	
with(merged_results,{table(ActivityMediaName, IR_ActMedia_FLAG)})









sites=as.data.frame(readxl::read_excel(translation_wb, 'masterSiteTable'))








## Data prep
Generating assessable dataset  

1. Assigning criteria (by parameter & use via criteria table)  
2. Convert to consistent units (target units defined by criteria)  
3. Check that data fractions & activities match assessment targets  
4. Aggregate to daily values  
5. Generate correction factors & calculate criteria  
6. Split data into assessment groups  
<br><br>

### Determine detection conditions and fill NDs
```{r, fill-masked}
merged_results_filled=fillMaskedValues(results=update_table_data, detquantlim=irdata$detquantlim, translation_wb=translation_wb,
									   detLimitTypeTable_sheetname="detLimitTypeTable", detLimitTypeTable_startRow=3,
									   unitConvTable_sheetname="unitConvTable", unitConvTable_startRow=1, unitConvTable_startCol=1,
									   lql_fac=0.5, uql_fac=1)
```


### Apply parameter translation table
```{r, apply-param-trans}
mrf_sub_translated=applyScreenTable(mrf_sub,wb=translation_wb,
									sheetname="paramTransTable",startRow=4,flag_col_name="IR_Parameter_FLAG",com_col_name="IR_Parameter_COMMENT",
									na_dup_err=F)
```
### Subset data to ACCEPT parameters
```{r, sub-accept-params}
accept_data=subset(mrf_sub_translated, IR_Parameter_FLAG=="ACCEPT")
```

```{r, echo=F}
tab=data.frame(table(droplevels(accept_data$CharacteristicName)))
names(tab)=c('Parameter', 'Count')
```
```{r, echo=F}
knitr::kable(tab, caption='Accepted parameter sample counts.')
```


