# Initial data processing

## Data validation
Functions to update & apply data validation tables, generate data with consistent nomenclature.  
1. Labs & activity types  
2. Activity media  
3. Parameter names & fractions  
4. Detection conditions  
5. Detection limit types  
6. Unit conversion factors  
7. Apply screening tables and subset to accepted data  

### Update screening/translation tables
#### Read initial site review and reject data from auto-rejected sites before updating
```{r, eval=F}
sites_auto_val=as.data.frame(readxl::read_excel('P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/02_site_validation/site-reviews-Jake-2019-08-02 2 ready for other reviews.xlsx', 'sites'))
mlids=sites_auto_val$MonitoringLocationIdentifier[sites_auto_val$IR_FLAG!='REJECT']
update_table_data=irdata$merged_results[irdata$merged_results$MonitoringLocationIdentifier %in% mlids,]
```

#### Update detection condition / limit name tables
```{r, update-detcondlim, eval=F}
updateDetCondLimTables(results=update_table_data, detquantlim=irdata$detquantlim, translation_wb=translation_wb,
						detConditionTable_startRow=3, detLimitTypeTable_startRow=3)
```

#### Update lab/activity & media tables
```{r, labactmedia, eval=F}
updateLabActMediaTables(update_table_data, translation_wb=translation_wb, labNameActivityTable_startRow = 2)
```

#### Update parameter translation tables
```{r, update-param-trans, eval=F}
updateParamTrans(data=update_table_data, detquantlim=irdata$detquantlim,  translation_wb=translation_wb, WQPParamCASID_startRow = 4)
```



### Apply pre-lim screening tables
1. Sites
2. Activity media
3. Lab/activity

```{r, apply-screens}
translation_wb='ir_translation_workbook_working_v9_ef - no IR_Fraction formula.xlsx'
merged_results=irdata$merged_results %>%
	applyScreenTable(wb=translation_wb, sheetname="masterSiteTable", startRow=1, flag_col_name="IR_Site_FLAG", com_col_name="IR_Site_COMMENT")
	rej_data=subset(merged_results, IR_Site_FLAG=='REJECT')
	acc_data=subset(merged_results, IR_Site_FLAG=='ACCEPT')
acc_data=acc_data%>% 
	applyScreenTable(wb=translation_wb, sheetname="activityMediaNameTable", startRow=1, flag_col_name="IR_ActMedia_FLAG", com_col_name="IR_ActMedia_COMMENT") %>% 
	applyScreenTable(wb=translation_wb, sheetname="labNameActivityTable", startRow=3, flag_col_name="IR_LabAct_FLAG", com_col_name="IR_LabAct_COMMENT") %>% 
	applyScreenTable(wb=translation_wb, sheetname="detConditionTable", startRow=3, flag_col_name="IR_DetCond_FLAG", com_col_name="IR_DetCond_COMMENT")

with(acc_data,{table(ActivityMediaName, IR_ActMedia_FLAG)})
rej_data_flag=subset(acc_data, IR_Site_FLAG=='REJECT' | IR_ActMedia_FLAG=='REJECT' | IR_LabAct_FLAG=='REJECT' | IR_DetCond_FLAG=='REJECT')
rej_data=plyr::rbind.fill(rej_data, rej_data_flag)
acc_data=subset(acc_data, IR_Site_FLAG=='ACCEPT' & IR_ActMedia_FLAG=='ACCEPT' & (IR_LabAct_FLAG=='ACCEPT' |  IR_LabAct_FLAG=='REVIEW') & IR_DetCond_FLAG=='ACCEPT')
rm(rej_data_flag)

any(acc_data$CharacteristicName=='Sulfate', na.rm=T)

dim(acc_data)
dim(rej_data)
dim(irdata$merged_results)
dim(merged_results)
```

### Determine detection conditions and fill NDs
```{r, fill-masked}
acc_data=fillMaskedValues(results=acc_data, detquantlim=irdata$detquantlim, translation_wb=translation_wb,
									   detLimitTypeTable_sheetname="detLimitTypeTable", detLimitTypeTable_startRow=3,
									   unitConvTable_sheetname="unitConvTable", unitConvTable_startRow=1, unitConvTable_startCol=1,
									   lql_fac=0.5, uql_fac=1)

```

### Back-fill units for data where unit was NA in data, but existed in detquantlim - add records w/o units in either to rejection dataframe
```{r, fill-units}
table(is.na(acc_data$ResultMeasure.MeasureUnitCode))
acc_data=within(acc_data, {
	ResultMeasure.MeasureUnitCode=ifelse(is.na(ResultMeasure.MeasureUnitCode) & !is.na(IR_Unit), as.character(IR_Unit), as.character(ResultMeasure.MeasureUnitCode))
	IR_Unit_FLAG=ifelse(!is.na(ResultMeasure.MeasureUnitCode), 'ACCEPT', 'REJECT')
	IR_Unit_Comment=ifelse(IR_Unit_FLAG=='ACCEPT', NA, 'No units available for data point')
})
table(acc_data$ResultMeasure.MeasureUnitCode)
table(is.na(acc_data$ResultMeasure.MeasureUnitCode))
unit_rej_data=subset(acc_data, IR_Unit_FLAG!='ACCEPT')
rej_data=plyr::rbind.fill(rej_data, unit_rej_data)
acc_data=subset(acc_data, IR_Unit_FLAG=='ACCEPT')
rm(unit_rej_data)
```

### Apply parameter translation table
```{r, param-trans}
acc_data=applyScreenTable(acc_data, wb=translation_wb, sheetname="paramTransTable", startRow=4, flag_col_name="IR_Parameter_FLAG", com_col_name="IR_Parameter_COMMENT")
table(acc_data$IR_Parameter_FLAG, exclude=NULL)
any(acc_data$R3172ParameterName=='Sulfate', na.rm=T)
```

### Rejecting data via parameter table, rbind rejected data back to rej_data
```{r, rej-param}
param_rej_data=subset(acc_data, IR_Parameter_FLAG=='REJECT')
rej_data=plyr::rbind.fill(rej_data, param_rej_data)
acc_data=subset(acc_data, IR_Parameter_FLAG=='ACCEPT' | IR_Parameter_FLAG=='REVIEW')
rm(param_rej_data)
table(droplevels(acc_data$ResultSampleFractionText), acc_data$IR_Fraction, exclude=NULL)
dim(acc_data)
dim(rej_data)
dim(merged_results)

table(is.na(acc_data$CAS))
any(acc_data$R3172ParameterName=='Sulfate', na.rm=T)
```

```{r, echo=F}
rm(list=c('nr','nr_sub','nr_na','irdata','merged_results'))
```

### Assign criteria
```{r, assign-crit}
acc_data_criteria=assignCriteria(acc_data, crit_wb='IR_uses_standards_working_v4_ef.xlsx', crit_sheetname='criteria', ss_sheetname='ss_criteria',
  crit_startRow = 3, ss_startRow = 4, rm_nocrit = TRUE, print = TRUE)
```

### Update unit conversion table
```{r, update-uct, eval=FALSE}
updateUnitConvTable(acc_data_criteria, translation_wb=translation_wb)
```

### Data prep
```{r, data-prep}
prepped_data=dataPrep(data=acc_data_criteria, translation_wb=translation_wb, cf_formulas_sheetname="cf_formulas", crit_wb="IR_uses_standards_working_v4_ef.xlsx", startRow_formulas=3)
objects(prepped_data)
```

















