# Toxics and conventionals assessments
## Define assessment grouping variables
```{r}
group_vars = c("IR_MLID", "IR_MLNAME", "IR_Lat", "IR_Long", "ASSESS_ID", "AU_NAME", "BeneficialUse", "BEN_CLASS",
	"CAS", "IRParameterName", "TargetFraction", "R3172ParameterName", "ParameterGroupName",
	"AsmntAggPeriod","AsmntAggPeriodUnit", "TableNumber","TableDescription","CriterionLabel","ParameterQualifier","SSC_MLID", "AsmntAggFun")
```

## Toxics
### General toxics
```{r}
toxics_exc=countExceedances(prepped_data$toxics, group_vars = group_vars)
toxics_assessed=assessExcCounts(toxics_exc, min_n=4, max_exc_count=1, max_exc_count_id=0)
with(toxics_assessed, {table(R3172ParameterName, IR_Cat)})
with(toxics_assessed, {table(ParameterGroupName, IR_Cat)})
```

### Radium
#### Cast to wide format & sum as appropriate
*All radium data are ND values*
```{r}
table(droplevels(prepped_data$radium$CharacteristicName))
table(prepped_data$radium$IR_DetCond)
radium_cast=reshape2::dcast(prepped_data$radium, IR_MLID+IR_MLNAME+IR_Lat+IR_Long+ASSESS_ID+AU_NAME+BeneficialUse+BEN_CLASS+CAS+IRParameterName+TargetFraction+R3172ParameterName+
					   ParameterGroupName+AsmntAggPeriod+AsmntAggPeriodUnit+TableDescription+CriterionLabel+ParameterQualifier+SSC_MLID+SSC_StartMon+SSC_EndMon+AsmntAggFun+ActivityStartDate~CharacteristicName, value.var='IR_Value')
any(!is.na(radium_cast$`Radium-226`) & !is.na(radium_cast$`Radium-228`))
```
*No sites/days with both Radium-226 & Radium-228. Only one assessable data point.*

## Conventionals
### General conventionals (need to remove turbidity assessments)
```{r}
conventionals_exc=countExceedances(prepped_data$conventionals, group_vars = group_vars)
conventionals_assessed=assessExcCounts(conventionals_exc, min_n=10, max_exc_pct=10, max_exc_count_id=1)
with(conventionals_assessed, {table(R3172ParameterName, IR_Cat)})
```

### Remove turbidity and assessed DO criteria
```{r}
conventionals_assessed=subset(conventionals_assessed, R3172ParameterName!='Turbidity Increase' & !(R3172ParameterName=='Minimum Dissolved Oxygen' & (AsmntAggPeriod==1 | AsmntAggPeriod==7)))
with(conventionals_assessed, {table(droplevels(R3172ParameterName), IR_Cat)})
```

### Lakes TDS
```{r}
lake_tds_exc=countExceedances(prepped_data$lakes_tds, group_vars = group_vars)
lake_tds_assessed=assessExcCounts(lake_tds_exc, min_n=2, max_exc_pct=10, max_exc_pct_id=0)
with(lake_tds_assessed, {table(R3172ParameterName, IR_Cat)})
```

### Site-specific mean TDS (Blue Creek)
```{r}
table(droplevels(prepped_data$agg_tds$ASSESS_ID), droplevels(prepped_data$agg_tds$AU_NAME))
mean(subset(prepped_data$agg_tds, NumericCriterion==4700)$IR_Value)
mean(subset(prepped_data$agg_tds, NumericCriterion==3800)$IR_Value)
ss_mean_tds_exc=countExceedances(prepped_data$agg_tds, group_vars = group_vars)
ss_mean_tds_assessed=assessExcCounts(ss_mean_tds_exc, min_n=10, max_exc_pct=50, max_exc_count_id=1)
ss_mean_tds_assessed
```



