# Gather & export preliminary assessments & data {#export-asmnts}

## Gather & bind assessments
### Internal assessments
```{r}
lake_profs_assessed=as.data.frame(readxl::read_excel('lake_profile_asmnts.xlsx', 'lake_profile_asmnts'))
# lake_profs_assessed=comb_asmnt_au
names(lake_profs_assessed)[names(lake_profs_assessed)=='au_param_Cat2020']='IR_Cat'
table(lake_profs_assessed$R3172ParameterName)
lake_profs_assessed=within(lake_profs_assessed, {
	R3172ParameterName=as.character(R3172ParameterName)
	R3172ParameterName[R3172ParameterName=='Dissolved oxygen (DO)']='Minimum Dissolved Oxygen'
	R3172ParameterName[R3172ParameterName=='Temperature, water']='Max. Temperature'
})
prelim_asmnts=plyr::rbind.fill(conventionals_assessed,lake_tds_assessed,ss_mean_tds_assessed,toxics_assessed, assessed_ecoli$ecoli_mlid_asmnts,lake_profs_assessed[,!names(lake_profs_assessed) %in% c('PrevCat','au_param_Cat2020','pot_delist','new_listing')])

# prelim_asmnts=plyr::rbind.fill(toxics_and_conventionals_assessments$conventionals_assessed, toxics_and_conventionals_assessments$toxics_assessed,lake_assessments$lake_tds_assessed, site_specific_tds_assessments$ss_mean_tds_assessed,assessed_ecoli$ecoli_mlid_asmnts,lake_profs_assessed[,!names(lake_profs_assessed) %in% c('PrevCat','au_param_Cat2020','pot_delist','new_listing')])
```

### One parameter-site rejection from secondary review
One site along the Provo River was rejected for dissolved oxygen readings because the sample pulls from the bottom of Deer Creek Reservoir (below dam).
```{r}
reject = data.frame(IR_MLID="UTAHDWQ_WQX-5913210",R3172ParameterName="Minimum Dissolved Oxygen",Remove = "1")
prelim_asmnts = merge(prelim_asmnts, reject, all.x = TRUE)
prelim_asmnts = subset(prelim_asmnts, is.na(prelim_asmnts$Remove))
prelim_asmnts = prelim_asmnts[,!names(prelim_asmnts)%in%c("Remove")]
```


### External assessments
This section adds the Great Salt Lake egg selenium, fish tissue mercury, high frequency dissolved oxygen, Snowbird, and E.coli advisory and sampling assessments. Note that per our meeting with Nick von Stackelberg on dissolved oxygen holding capacity in high elevation waters, we are only assessing the 30-day average this cycle for the high frequency assessment.

Additionally, the Snowbird assessments occur at sites that are not included within the master site file because they did not come through the WQP.
```{r, eval = F}
gsl_egg_se_assessed=as.data.frame(readxl::read_excel('P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/99_external_assessments/gsl_egg_se/gsl_egg_se_assessment.xlsx', 'asmnt'))
names(gsl_egg_se_assessed)[names(gsl_egg_se_assessed)=='AssessCat']='IR_Cat'
fish_hg_assessed=as.data.frame(readxl::read_excel('P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/99_external_assessments/fish_tissue/3_draft_fishtissue_hgassessment_v2_ef.xlsx', 'asmnt'))
fish_hg_assessed=fish_hg_assessed[,!names(fish_hg_assessed) %in% 'Category to Report']
names(fish_hg_assessed)[names(fish_hg_assessed)=='AssessCat']='IR_Cat'
hfdo_assessed=as.data.frame(readxl::read_excel('P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/99_external_assessments/hfdo/hfdo_assessed_review.xlsx', 'HFDO_asmnts'))
hfdo_assessed = subset(hfdo_assessed, hfdo_assessed$AsmntAggPeriod==30)
hfdo_assessed$R3172ParameterName='High frequency DO'
hfdo_assessed=irTools::rollUp(list(hfdo_assessed), group_vars = c("BEN_CLASS","IR_MLID","IR_MLNAME","IR_Lat","IR_Long","ASSESS_ID", "AU_NAME", "R3172ParameterName","BeneficialUse"), expand_uses=F, print=F)
hfdo_assessed=within(hfdo_assessed, {
	IR_Lat=wqTools::facToNum(IR_Lat)
	IR_Long=wqTools::facToNum(IR_Long)
})
names(hfdo_assessed)[names(hfdo_assessed)=='AssessCat']='IR_Cat'
ecoli_adv_assessed=as.data.frame(readxl::read_excel('P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/99_external_assessments/ecoli/3_draft_ecoliadvisory_assessment_v3_ef.xlsx', 'Sheet1'))
names(ecoli_adv_assessed)[names(ecoli_adv_assessed)=='AssessCat']='IR_Cat'
snowbird_assessed=as.data.frame(readxl::read_excel('P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/99_external_assessments/snowbird/snowbird_asmnt.xlsx', 'asmnt'))
names(snowbird_assessed)[names(snowbird_assessed)=='AssessCat']='IR_Cat'
snowbird_assessed=within(snowbird_assessed, {
	IR_Lat=wqTools::facToNum(IR_Lat)
	IR_Long=wqTools::facToNum(IR_Long)
})
snowbird_assessed = snowbird_assessed[,!names(snowbird_assessed)%in%c("Mgmt_Unit")]
bugs_assessed=as.data.frame(readxl::read_excel("P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/99_external_assessments/macroinvertebrates/1_draftanalysis_macroinvert_oeassessment_AssessNotes_v4_ef.xlsx", '18-20 final assessments'))
bugs_assessed = bugs_assessed[,c("ASSESS_ID","OriginalAssessCat","IR Note1","2016AssessCat","Category to Report")]
names(bugs_assessed) = c("ASSESS_ID","OrigAssessCat_Bugs","EF_KF_BH_Note_Bugs","2016AssessCat_Bugs","IR_Cat")
bugs_assessed = subset(bugs_assessed, !bugs_assessed$ASSESS_ID=="(blank)")
bugs_assessed$R3172ParameterName = "Macroinvertebrates"
# Get bug beneficial uses
bugs_latlong=as.data.frame(readxl::read_excel("P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/99_external_assessments/macroinvertebrates/1_draftanalysis_macroinvert_oeassessment_AssessNotes_v4_ef.xlsx", '18-20 data assessments'))
bugs_latlong = unique(bugs_latlong[!is.na(bugs_latlong$DD_LAT_Y),c("DD_LAT_Y","DD_LONG_X")])
au_info = wqTools::assignAUs(bugs_latlong, lat = "DD_LAT_Y", long = "DD_LONG_X")
au_bu_info = wqTools::assignUses(au_info, lat = "DD_LAT_Y", long = "DD_LONG_X")
au_bu_wmu_info = wqTools::assignPolys("wmu_poly", columns = c("Mgmt_Unit"), au_bu_info, lat = "DD_LAT_Y", long = "DD_LONG_X")
au_bu_wmu_info = unique(au_bu_wmu_info[!is.na(au_bu_wmu_info$ASSESS_ID),c("ASSESS_ID","AU_NAME","Water_Type","BeneficialUse","Mgmt_Unit")])
bugs_assessed = merge(bugs_assessed, au_bu_wmu_info, all.x = TRUE)
bugs_assessed = subset(bugs_assessed, !bugs_assessed$ASSESS_ID%in%c("undefined"))
names(bugs_assessed)[names(bugs_assessed)=="BeneficialUse"] = "BEN_CLASS"
names(bugs_assessed)[names(bugs_assessed)=="Water_Type"] = "AU_Type"
bugs_assessed$BeneficialUse = gsub("1C,|2A,|2B,|4","",bugs_assessed$BEN_CLASS)
bugs_assessed$BeneficialUse = gsub(",$","",bugs_assessed$BeneficialUse)
bugs_assd_flat = tidyr::separate(data = bugs_assessed, col = BeneficialUse, into = c("BenUse1", "BenUse2"), sep = ",")
bugs_assd_flat = tidyr::pivot_longer(bugs_assd_flat, cols = c("BenUse1","BenUse2"), values_to = "BeneficialUse")
bugs_assd_flat = bugs_assd_flat[!is.na(bugs_assd_flat$BeneficialUse),!names(bugs_assd_flat)%in%c("name")]
bugs_assd_flat$IR_MLID = paste0(bugs_assd_flat$AU_NAME,"-Bugs")
bugs_assd_flat$IR_MLNAME = paste0(bugs_assd_flat$AU_NAME,"-Bugs")

habs_assessed = as.data.frame(readxl::read_excel("P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/99_external_assessments/hab/3_draft_habassessment_v1_kf.xlsx", "rolledUp_AU"))
au_bu_wmu = unique(acc_data_criteria[!is.na(acc_data_criteria$BEN_CLASS),c("ASSESS_ID","BEN_CLASS","Mgmt_Unit","AU_Type")])
habs_assessed = merge(habs_assessed, au_bu_wmu, all.x = TRUE)
habs_assessed$BEN_CLASS[habs_assessed$AU_NAME=="Upper Kents Lake"] = "2B,3A,4"
habs_assessed$Mgmt_Unit[habs_assessed$AU_NAME=="Upper Kents Lake"] = "Cedar-Beaver"
habs_assessed$AU_Type[habs_assessed$AU_NAME=="Upper Kents Lake"] = "Reservoir/Lake"
habs_assessed$BEN_CLASS[habs_assessed$AU_NAME=="Dry Gulch Creek"] = "1C,2B,3E,4"
habs_assessed$Mgmt_Unit[habs_assessed$AU_NAME=="Dry Gulch Creek"] = "Uinta Basin"
habs_assessed$AU_Type[habs_assessed$AU_NAME=="Dry Gulch Creek"] = "River/Stream"
habs_assessed$IR_MLID = paste0(habs_assessed$AU_NAME,"-HABs")
habs_assessed$IR_MLNAME = paste0(habs_assessed$AU_NAME,"-HABs")
habs_assessed$BeneficialUse = "2A"
habs_assessed$BeneficialUse = ifelse(grepl("2B", habs_assessed$BEN_CLASS),"2B","2A")
names(habs_assessed)[names(habs_assessed)=='AssessCat']='IR_Cat'


external_asmnts=plyr::rbind.fill(gsl_egg_se_assessed, fish_hg_assessed, hfdo_assessed, ecoli_adv_assessed, snowbird_assessed, bugs_assd_flat, habs_assessed)
save(external_asmnts, file = "external_assessments_v4.RData") # latest version: Aug 2, 2020
```

#### Combined assessments
```{r}
load("external_assessments_v4.RData") # remember to change if any changes occur to external assessments
prelim_asmnts=plyr::rbind.fill(prelim_asmnts, external_asmnts)
prelim_asmnts$pol_ind=ifelse(prelim_asmnts$ParameterGroupName=='POLLUTION INDICATORS' | prelim_asmnts$R3172ParameterName=='Lakes tier II', 'Y', 'N')
prelim_asmnts$pol_ind[is.na(prelim_asmnts$pol_ind)]='N'
any(is.na(prelim_asmnts$IR_Cat))
```

### Assign review metadata
#### WMUs
```{r}
prelim_asmnts_wmus = subset(prelim_asmnts, !is.na(prelim_asmnts$Mgmt_Unit))
prelim_asmnts_nowmus = subset(prelim_asmnts, is.na(prelim_asmnts$Mgmt_Unit))
prelim_asmnts_nowmus = prelim_asmnts_nowmus[,!names(prelim_asmnts_nowmus)%in%c("Mgmt_Unit","AU_Type")]
wmus=unique(acc_data_criteria[,c('ASSESS_ID','AU_Type','Mgmt_Unit')])
dim(prelim_asmnts)
prelim_asmnts_nowmus=merge(prelim_asmnts_nowmus, wmus, all.x=T)
prelim_asmnts=plyr::rbind.fill(prelim_asmnts_wmus, prelim_asmnts_nowmus)
dim(prelim_asmnts)
prelim_asmnts$Mgmt_Unit[prelim_asmnts$BeneficialUse=='5A']='Great Salt Lake'
any(is.na(prelim_asmnts$Mgmt_Unit))
```

#### Lakes
```{r}
prelim_asmnts$lake=ifelse(prelim_asmnts$AU_Type=='Reservoir/Lake' | prelim_asmnts$BeneficialUse=='5A', 'Y', 'N')
table(prelim_asmnts$lake, exclude=NULL)
```

#### Reviewer export file
```{r}
compiled_data = irTools::composeExport(prepped_data = prepped_data, toxics_assessed = toxics_assessed, conventionals_assessed = conventionals_assessed, create_workbooks = FALSE, include_rejected = FALSE)
save(compiled_data, file = "reviewer_export_data.Rdata")
```

#### Export all site-use-parameter assessments
```{r}
# Rename some objects to make them easier to remember and use
assessed_dat_crit_flat = prepped_data$acc_data
assessed_dat_allcols = subset(acc_data, acc_data$ResultIdentifier%in%unique(assessed_dat_crit_flat$ResultIdentifier))

lake_assessments = list(lake_tds_assessed=lake_tds_assessed,lake_tds_exc=lake_tds_exc,lake_profs_assessed=lake_profs_assessed)
site_specific_tds_assessments = list(ss_mean_tds_assessed=ss_mean_tds_assessed, ss_mean_tds_exc=ss_mean_tds_exc)
toxics_and_conventionals_assessments = list(conventionals_assessed=conventionals_assessed, conventionals_exc=conventionals_exc, toxics_assessed=toxics_assessed, toxics_exc=toxics_exc)

save(acc_data_criteria, assessed_dat_crit_flat,assessed_dat_allcols,group_vars, lake_assessments, site_specific_tds_assessments, toxics_and_conventionals_assessments, prepped_data, assessed_ecoli, prelim_asmnts, compiled_data, file='prelim_asmnts_data.Rdata')
```

## Secondary review input files
#### Permits
```{r, eval = FALSE, echo = FALSE}
# permits=as.data.frame(readxl::read_excel("P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/08_secondary_reviews/Permits/Current UPDES permits w_WLAs.xlsx", 'permits'))
# save(permits, file = "current_updes_permits.RData")

```

```{r, permits}
load("current_updes_permits.RData")
ut_fac1=wqTools::readECHO_fac(p_st="ut", p_act="y")
fac_coords1=do.call(rbind.data.frame,ut_fac1$geometry$coordinates)
names(fac_coords1)=c("dec_long","dec_lat")
fac_coords1=data.frame(ut_fac1$properties[,c("SourceID","CWPName","CWPFacilityTypeIndicator")], (fac_coords1))

permits2=subset(permits, !PermitID %in% ut_fac1$properties$SourceID)
ut_fac2=wqTools::readECHO_fac(p_pid=permits2$PermitID)
fac_coords2=do.call(rbind.data.frame,ut_fac2$geometry$coordinates)
names(fac_coords2)=c("dec_long","dec_lat")
fac_coords2=data.frame(ut_fac2$properties[,c("SourceID","CWPName","CWPFacilityTypeIndicator")], (fac_coords2))

ut_fac=rbind(fac_coords1, fac_coords2)
names(ut_fac)[names(ut_fac)=="SourceID"]="locationID"
names(ut_fac)[names(ut_fac)=="CWPName"]="locationName"
names(ut_fac)[names(ut_fac)=="CWPFacilityTypeIndicator"]="locationType"
names(ut_fac)[names(ut_fac)=="dec_long"]="LongitudeMeasure"
names(ut_fac)[names(ut_fac)=="dec_lat"]="LatitudeMeasure"

ut_fac=wqTools::assignAUs(ut_fac)
ut_fac$priority=ifelse(ut_fac$locationID %in% permits$PermitID, 'Y', 'N')
permits_aus=subset(ut_fac, locationID %in% permits$PermitID)

prelim_asmnts$permit=ifelse(prelim_asmnts$ASSESS_ID %in% permits_aus$ASSESS_ID, 'Y','N')
table(prelim_asmnts$permit, exclude=NULL)

write.csv(file='ut_facilities.csv', ut_fac, row.names=F)
```

#### New listings (AU-parameter scale)
```{r}
prelim_asmnts$new_listing=NA
current_listings=read.csv(file='current_listings.csv')
prelim_asmnts=merge(prelim_asmnts, current_listings, all.x=T)
prelim_asmnts$new_listing=ifelse(prelim_asmnts$pol_ind=='N' & prelim_asmnts$IR_Cat=='NS' & is.na(prelim_asmnts$AU_EPACat), 'Y', 'N')
table(prelim_asmnts$new_listing, exclude=NULL)
prelim_asmnts$confirmed_listing=ifelse(prelim_asmnts$pol_ind=='N' & prelim_asmnts$IR_Cat=='NS' & !is.na(prelim_asmnts$AU_EPACat), 'Y', 'N')
table(prelim_asmnts$confirmed_listing, exclude=NULL)
prelim_asmnts=prelim_asmnts[,!names(prelim_asmnts) %in% c('AU_EPACat','PARAM_NAME')]
```

### Export files 
```{r}
site_use_param_asmnt=irTools::rollUp(list(prelim_asmnts), group_vars = c("BEN_CLASS","IR_MLID","IR_MLNAME","IR_Lat","IR_Long","ASSESS_ID","AU_NAME", "R3172ParameterName", "BeneficialUse", "pol_ind", "Mgmt_Unit","lake","permit","new_listing"), expand_uses=F)

site_use_param_asmnt=within(site_use_param_asmnt, {
	site_param_review=NA
	site_param_review[new_listing=='Y' & permit=='Y' & pol_ind=='N'] = 5
	site_param_review[new_listing=='Y' & permit=='N' & pol_ind=='N'] = 4
	site_param_review[new_listing=='N' & permit=='Y'] = 3
	site_param_review[new_listing=='N' & permit=='N'  & pol_ind=='N' & AssessCat=='IDEX' & !ASSESS_ID %in% subset(site_use_param_asmnt, site_param_review %in% c('New listing, permit', 'New listing'))$ASSESS_ID] = 2
	site_param_review[is.na(site_param_review)] = 1
})
table(site_use_param_asmnt$site_param_review, exclude=NULL)
au_revs=unique(site_use_param_asmnt[,c('ASSESS_ID','site_param_review')])
au_revs=aggregate(site_param_review~ASSESS_ID, au_revs, 'max')
names(au_revs)[names(au_revs)=='site_param_review']='au_rev'
site_use_param_asmnt=merge(site_use_param_asmnt, au_revs, all.x=T)

site_use_param_asmnt=within(site_use_param_asmnt, {
	AU_review=NA
	AU_review[au_rev==5]='New listing, permit'
	AU_review[au_rev==4]='New listing'
	AU_review[au_rev==3]='Permit'
	AU_review[au_rev==2]='New insufficient data w/ exc'
	AU_review[au_rev==1]='Review needed, low priority'
})
table(site_use_param_asmnt$AU_review, exclude=NULL)
write.csv(file='site_use_param_asmnt.csv', site_use_param_asmnt, row.names=F)
```

#### Secondary review input files
```{r, eval = F}
au_splits=as.data.frame(readxl::read_excel('site-use-param-asmnt-blank.xlsx', 'au-splits'))
au_reviews=as.data.frame(readxl::read_excel('site-use-param-asmnt-blank.xlsx', 'au-reviews'))
site_reviews=as.data.frame(readxl::read_excel('site-use-param-asmnt-blank.xlsx', 'site-reviews'))
record_reviews=as.data.frame(readxl::read_excel('site-use-param-asmnt-blank.xlsx', 'record-reviews'))
sw_reviews=as.data.frame(readxl::read_excel('site-use-param-asmnt-blank.xlsx', 'sw-reviews'))
# plyr::d_ply(site_use_param_asmnt, 'Mgmt_Unit',
# 	function(sdf) writexl::write_xlsx(list(
# 										`site-use-param-asmnt`=sdf, 
# 										`au-splits`=au_splits,
# 										`au-reviews`=au_reviews,
# 										`site-reviews`=site_reviews,
# 										`sw-reviews`=sw_reviews,
# 										`record-reviews`=record_reviews
# 	), path=paste0('secondary-review-input-', sdf$Mgmt_Unit[1], '.xlsx'), format_headers=F, col_names=T))

writexl::write_xlsx(list(
										`site-use-param-asmnt`=site_use_param_asmnt, 
										`au-splits`=au_splits,
										`au-reviews`=au_reviews,
										`site-reviews`=site_reviews,
										`sw-reviews`=sw_reviews,
										`record-reviews`=record_reviews
	), path=paste0('secondary-review-input-all.xlsx'), format_headers=F, col_names=T)
```

### Write asmntDashboard_data
*Currently excluding GSL egg, fish Hg, HFDO, macroinvertebrate, & lake profile data. These can be reviewed in other capacities.*
#### Plot data
```{r}
assessed_data=unique(prepped_data$acc_data[,c("CAS", "ResultIdentifier","ActivityStartDate", "IR_MLID", "IR_MLNAME", "ASSESS_ID", "AU_NAME", 
									"AU_Type", "BEN_CLASS", "IRParameterName", "R3172ParameterName", "IR_Value", "IR_Unit", "CriterionUnits",
									"IR_DetCond", "IR_Fraction", "IR_ActivityType", "IR_Lat", "IR_Long", 
									"DataLoggerLine", "ActivityRelativeDepthName", "ActivityDepthHeightMeasure.MeasureValue", 
									"R317Descrp", "ActivityDepthHeightMeasure.MeasureUnitCode")
					])
criteria=unique(prepped_data$acc_data[,c("CAS", "ActivityStartDate", "IR_MLID", "IR_MLNAME", "BeneficialUse", 
   								"R3172ParameterName", "CriterionUnits", "TargetFraction", "CriterionLabel", 
   								"CriterionType", "NumericCriterion","TableDescription", "ParameterQualifier", 
   								"FrequencyCombined", "FrequencyNumber", "FrequencyUnit", "TargetActivityType")
				])
criteria=subset(criteria, !BeneficialUse %in% c('CF', 'SUP'))
```

##### Build criteria labels
```{r}
criteria=within(criteria, {
	bu=ifelse(TableDescription=='LIST OF HUMAN HEALTH CRITERIA (CONSUMPTION)', paste0('HH-',BeneficialUse), BeneficialUse)
	frac=tolower(TargetFraction)
	els=ifelse(ParameterQualifier %in% c('early life stages are present','Fish Early Life Stages are Present'), 'ELS', NA)
	acc_chron=ifelse(CriterionLabel =='Acute', 'acute', 'chronic')
	ts=ifelse(R3172ParameterName=='Minimum Dissolved Oxygen' | R3172ParameterName=='E. coli', paste0(FrequencyNumber, ' day ', tolower(FrequencyCombined)), NA)
	ts=gsub('NA day', 'daily', ts)
	ts=gsub('average', 'avg', ts)
	ts=gsub('minimum', 'min', ts)
	label=paste(bu, R3172ParameterName, ts, els, acc_chron, frac) 
	label=gsub('Minimum Dissolved Oxygen', 'DO', label)
	label=gsub('Max. Temperature', 'Temperature', label)
	label=gsub(' NA', '', label)
	label=gsub('dissolved', '(diss)', label)
	label=gsub('total', '(tot)', label)
	label=gsub('none', '', label)
	label=gsub('daily maximum', 'max', label)
	label=gsub('geometric mean', 'geomean', label)
	label=ifelse(R3172ParameterName=='pH' | R3172ParameterName=='Total Dissolved Solids', paste(label, CriterionType), label)
})
head(subset(criteria, R3172ParameterName=='Total Dissolved Solids'))

criteria=criteria[,!names(criteria) %in% c('ts','acc_chron','els','frac','bu')]
save(assessed_data, criteria, file='asmntDashboard_data.Rdata')
```

#### Write assessment Excel file
```{r, eval=TRUE}
writexl::write_xlsx(list(
						site_use_param_asmnt=site_use_param_asmnt,
						prelim_asmnts=prelim_asmnts,
						lake_prof_asmnts=lake_profs_assessed,
						conventionals=subset(prepped_data$acc_data, AssessmentType=='Conventional'),
						toxics=subset(prepped_data$acc_data, AssessmentType=='Toxic'),
						supplement=subset(prepped_data$acc_data, AssessmentType=='All'),
						ecoli=subset(prepped_data$acc_data, AssessmentType=='Ecoli')
					),
		path = 'prelim_asmnts.xlsx', format_headers=F, col_names=T)
```


```{r, eval=F}
data=prepped_data$toxics
data$NumericCriterion=wqTools::facToNum(data$NumericCriterion)
data=within(data, {
	bu=ifelse(TableDescription=='LIST OF HUMAN HEALTH CRITERIA (CONSUMPTION)', paste0('HH-',BeneficialUse), BeneficialUse)
	frac=tolower(TargetFraction)
	els=ifelse(ParameterQualifier %in% c('early life stages are present','Fish Early Life Stages are Present'), 'ELS', NA)
	acc_chron=ifelse(CriterionLabel =='Acute', 'acute', 'chronic')
	ts=ifelse(R3172ParameterName=='Minimum Dissolved Oxygen' | R3172ParameterName=='E. coli', paste0(FrequencyNumber, ' day ', tolower(FrequencyCombined)), NA)
	ts=gsub('NA day', 'daily', ts)
	ts=gsub('average', 'avg', ts)
	ts=gsub('minimum', 'min', ts)
	label=paste(bu, R3172ParameterName, ts, els, acc_chron, frac) 
	label=gsub('Minimum Dissolved Oxygen', 'DO', label)
	label=gsub('Max. Temperature', 'Temperature', label)
	label=gsub(' NA', '', label)
	label=gsub('dissolved', '(diss)', label)
	label=gsub('total', '(tot)', label)
	label=gsub('none', '', label)
	label=gsub('daily maximum', 'max', label)
	label=gsub('geometric mean', 'geomean', label)
	label=ifelse(R3172ParameterName=='pH' | R3172ParameterName=='Total Dissolved Solids', paste(label, CriterionType), label)
})

library(plotly)
plot_data=unique(data[data$R3172ParameterName!='Pentachlorophenol' & data$R3172ParameterName!='Total Ammonia as N',c('NumericCriterion','hardness','R3172ParameterName','CriterionLabel')])
plot_data=dplyr::sample_frac(plot_data, 0.1)
plot_data$label=paste(plot_data$R3172ParameterName, tolower(plot_data$CriterionLabel))
hardness_dep_crit_plot=plot_ly(data=plot_data) %>%
	add_lines(x=~hardness, y=~NumericCriterion, color=~label) %>%
		layout(
			title = "Hardness dependent criteria",
			xaxis = list(title = "Hardness (mg/L)"),
			yaxis = list(side = 'left', title = 'Criterion (ug/L)')#,
			#legend = list(x = 0.01, y = 0.99)
		) %>% 
		config(displaylogo = FALSE,
			modeBarButtonsToRemove = c(
				'sendDataToCloud',
				'hoverClosestCartesian',
				'hoverCompareCartesian',
				'lasso2d',
				'select2d'
			)
		)
#hardness_dep_crit_plot
#save(file='C:/Users/jvander/Documents/R/dwq-R-tools-presentation/figures/hardness_dep_crit.Rdata', hardness_dep_crit_plot)
#htmlwidgets::saveWidget(hardness_dep_crit_plot, file='C:/Users/jvander/Documents/R/dwq-R-tools-presentation/figures/hardness_dep_crit.html')
api_create(hardness_dep_crit_plot, filename="hardness-dep-crit")
```
