# Roll up assessments to various levels {#rollup-asmnts}

## Remove Lakes and Reservoirs
```{r}
asmts_sr = subset(prelim_asmnts, !prelim_asmnts$AU_Type%in%c("Reservoir/Lake"))
```

## Remove Pollution Indicators
Pollution indicators must be removed from roll up to ensure assessment units are assessed appropriately

```{r}
pi_recs = subset(asmts_sr, asmts_sr$ParameterGroupName=="POLLUTION INDICATORS")
pi_recs$pi = 1
asmnts_no_pi = merge(asmts_sr, pi_recs, all.x=TRUE)
asmnts_no_pi = subset(asmnts_no_pi, is.na(asmnts_no_pi$pi))
asmnts_no_pi = asmnts_no_pi[,!names(asmnts_no_pi)%in%c("pi")]
rm(pi_recs)
```

## Generate 303d and 305b lists

### Add AU Resegmentation Data
```{r, eval = F, echo = F}
# AU Resegmentation data
# au_reseg = readxl::read_xlsx("C:\\Users\\ehinman\\Downloads\\site_au_reseg (2).xlsx", sheet = "Resegment AUs")
# names(au_reseg)[names(au_reseg)=="AUID2016"] = "ASSESS_ID2016"
# names(au_reseg)[names(au_reseg)=="AUNAME2016"] = "AU_NAME2016"
# save(au_reseg, file = "au_resegmentation.RData")
load("au_resegmentation.RData")
```

### Add Historical Assessments
```{r, eval = F, echo = F}
# # 2016 IR Categories for 305b and 303d to carry forward previous info
# tofb = readxl::read_xlsx("C:\\Users\\ehinman\\Documents\\GitHub\\IR-2020\\cyc_last_assessed_first_listed.xlsx", sheet = "website_2016_305b")
# tofb = merge(tofb, au_reseg[,c("ASSESS_ID","ASSESS_ID2016")], all.x=TRUE)
# tofb$ASSESS_ID = ifelse(is.na(tofb$ASSESS_ID),tofb$ASSESS_ID2016, tofb$ASSESS_ID)
# names(tofb)[names(tofb)=="FINAL_AU_EPACat"] = "AU_EPACat"
# 
# totd = readxl::read_xlsx("C:\\Users\\ehinman\\Documents\\GitHub\\IR-2020\\cyc_last_assessed_first_listed.xlsx", sheet = "website_2016_303d")
# totd = unique(totd)
# 
# totd1 = totd%>%separate(Parameter_Cat5NDUses,c("use1","use2","use3","use4"),sep="; ")%>%pivot_longer(cols = c(use1,use2,use3,use4), names_to = "use",values_to = "BeneficialUse",values_drop_na=TRUE)
# totd1 = unique(totd1)
# 
# totd1$BeneficialUse = gsub("HH","",totd1$BeneficialUse)
# 
# 
# conv = data.frame(Param_frac_AbbrevName=unique(totd1$Param_frac_AbbrevName), R3172ParameterName = c("E. coli","Max. Temperature","pH","Total Dissolved Solids","Macroinvertebrates","Minimum Dissolved Oxygen","Sediment","Aluminum","Selenium","Radium 226, 228 (Combined)","Cadmium","Iron","Lead","Copper","Mercury","Boron","Total Ammonia as N","Zinc","Arsenic","Total Phosphorus as P","Nitrates as N"))
# 
# totd1 = merge(totd1, conv, all.x = TRUE)
# totd1 = merge(totd1, au_reseg, all.x = TRUE)
# totd1$ASSESS_ID = ifelse(is.na(totd1$ASSESS_ID),totd1$ASSESS_ID2016,totd1$ASSESS_ID)
# 
# totd = totd1[,!names(totd1)%in%c("AU_Type","AU_NAME","AU_NAME2016","AU_DESCRIP","use","Param_frac_AbbrevName","EPAs Approved TMDL ID","IRReport","EPA Cause ID","AU_DWQCat","Parameter_DWQCat","RESEG2020")]
# totd = unique(totd)
# 
# fa = readxl::read_xlsx("C:\\Users\\ehinman\\Documents\\GitHub\\IR-2020\\cyc_last_assessed_first_listed.xlsx", sheet = "website_2016_4A")
# 
# fa1 = fa%>%separate(Parameter_Cat5NDUses,c("use1","use2","use3","use4"),sep="; ")%>%pivot_longer(cols = c(use1,use2,use3,use4), names_to = "use",values_to = "BeneficialUse",values_drop_na=TRUE)
# 
# fa1$BeneficialUse = gsub("HH","",fa1$BeneficialUse)
# 
# conv = data.frame(Param_frac_AbbrevName=unique(fa1$Param_frac_AbbrevName), R3172ParameterName = c("Total Phosphorus as P","Minimum Dissolved Oxygen","Total Ammonia as N","Max. Temperature","Selenium","Gross Alpha","Total Dissolved Solids","Sediment","E. coli","Zinc","Boron","Cadmium"))
# 
# fa1 = merge(fa1, conv, all.x = TRUE)
# fa1 = merge(fa1, au_reseg, all.x = TRUE)
# fa1$ASSESS_ID = ifelse(is.na(fa1$ASSESS_ID),fa1$ASSESS_ID2016,fa1$ASSESS_ID)
# 
# fa1 = unique(fa1[,names(fa1)%in%c("ASSESS_ID","R3172ParameterName","BeneficialUse","CycleFirstListed","TMDL ID")])
# 
# save(totd,tofb,fa1, file = "2016_305b_303d_4a.RData")
load("2016_305b_303d_4a.Rdata")
```

### AU Description Info
```{r}
# Add AU info
au_auid_audesc = data.frame(ASSESS_ID = wqTools::au_poly$ASSESS_ID, AU_NAME = wqTools::au_poly$AU_NAME, AU_DESCRIP = wqTools::au_poly$AU_DESCRIP)

# Add WMU info
load("au_wmu.RData")

# Add Stream miles
# au_geom = read.csv("P:\\WQ\\Integrated Report\\IR_2020\\2020-IR-assessments\\spatial_files\\au_geometry.csv")
# au_geom = au_geom[,!names(au_geom)%in%c("X")]
# save(au_geom, file = "au_geometry.RData")
load("au_geometry.RData")
```

### Add Delistings

```{r}
# delistings = readxl::read_xlsx("C:\\Users\\ehinman\\Downloads\\z_delisting_template_forEH.xlsx", sheet = "Draft 2018 2020 IR delistings")
# names(delistings)[names(delistings)=="ASSESS_ID"] = "ASSESS_ID2016"

# delistings = merge(delistings, au_reseg, all.x = TRUE)
# delistings = subset(delistings, is.na(delistings$`EF Note`))
# delistings$ASSESS_ID = ifelse(is.na(delistings$ASSESS_ID),delistings$ASSESS_ID2016,delistings$ASSESS_ID)
# 
# 
# delistings = delistings[,c("ASSESS_ID","R3172ParameterName","desliting_notes")]
# names(delistings)[names(delistings)=="desliting_notes"] = "delisting_notes"
# save(delistings, file = "delistings.RData")

# au_parm_cats_D = merge(au_param_cats_rolling, delistings, all = TRUE)
# write.csv(au_parm_cats_D, "au_param_cats_delistings.csv")
load("delistings.RData") # delistings incorporate the au-resegmentation results.
delistings = merge(delistings, au_auid_audesc, all.x = TRUE)
delistings = merge(delistings, au_wmu, all.x = TRUE)

# delistings_abbrev = delistings[,c("ASSESS_ID","R3172ParameterName","delisting_notes")]
# tmdl_abbrev = unique(tmdls[,c("ASSESS_ID","TMDL ID","R3172ParameterName")])
# tmdl_delistings = merge(tmdl_abbrev, delistings_abbrev, all.x = TRUE)
# rm(tmdl_abbrev, tmdl_delistings, delistings_abbrev)
```


### Add TMDLs
TMDL data from the following file:
"P:\WQ\Integrated Report\IR_2020\approved_tmdls\Approved_TMDLs_08122019_v3.xlsx"
```{r}
load("tmdls_2020_ir.Rdata")
parm_trans = data.frame("Impaired Parameter" = unique(tmdls$`Impaired Parameter`), R3172ParameterName = c("Minimum Dissolved Oxygen","Total Phosphorus as P","Max. Temperature","Sediment","Selenium","Total Dissolved Solids","Gross Alpha","Total Nitrogen","E. coli","Zinc","pH","Total Coliform","Boron","Cadmium","Total Ammonia as N"))

names(tmdls)[names(tmdls)=="Assessment Unit ID"] <- "ASSESS_ID2016"
names(tmdls)[names(tmdls)=="Impaired Parameter"] = "Impaired.Parameter"

tmdls = merge(tmdls, parm_trans, all.x = TRUE)
tmdls = merge(tmdls, au_reseg, all.x = TRUE)
tmdls$ASSESS_ID = ifelse(is.na(tmdls$ASSESS_ID),tmdls$ASSESS_ID2016, tmdls$ASSESS_ID)

tmdls = tmdls[,!names(tmdls)%in%c("AU_NAME","AU_DESCRIP","AU_Type","AU_NAME2016","RESEG2020")]
tmdls = merge(tmdls, au_auid_audesc, all.x = TRUE)
tmdls = merge(tmdls, au_wmu, all.x = TRUE)
tmdls = merge(tmdls, au_geom[,c("ASSESS_ID","au_stream_len_miles", "au_area_acres","AU_Type")], all.x = TRUE)
```

### 303d

The 303d list is a mix of past and present impairments. The first step is to find all impaired AU-parameter combinations from the 2018/2020 cycle. The next step is to roll in historical Cat5's before checking to see which of those historical Cat5's are part of the delisting analysis. Then, once those have been removed from the 303d list, the next step is to incorporate TMDLs into the 303d list. AU-parameter combinations that are covered by a TMDL are removed from the 303d list. However, AU's with a TMDL and a new or historical impairment not included in the TMDL are kept on the 303d list and listed as Cat5 on the 305b list. The outcome of the 303d list must be incorporated in the 305b list, so that list is composed second.

```{r}
# Find Cat5's from 2018/2020
ns_param_asmnts = irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME","BeneficialUse", "R3172ParameterName"), cat_var="IR_Cat", expand_uses=F, print=F)
ns_param_asmnts$ASSESS_ID = as.character(ns_param_asmnts$ASSESS_ID)
names(ns_param_asmnts)[names(ns_param_asmnts)=="AssessCat"]="param_DWQasmnt"
ns_param_asmnts = subset(ns_param_asmnts, ns_param_asmnts$param_DWQasmnt=="NS")
ns_param_asmnts$Parameter_EPACat_2020 = 5

# ns_param_asmnts = merge(ns_param_asmnts, au_reseg, all.x = TRUE)
# ns_param_asmnts$ASSESS_ID2016=ifelse(is.na(ns_param_asmnts$ASSESS_ID2016),ns_param_asmnts$ASSESS_ID,ns_param_asmnts$ASSESS_ID2016)
# ns_param_asmnts = ns_param_asmnts[,!names(ns_param_asmnts)%in%c("AU_NAME2016","ASSESS_ID2016","AU_Type","AU_DESCRIP","RESEG2020")]

totd = unique(totd[,!names(totd)%in%c("AU_EPACat","ASSESS_ID2016","IRCycleAULastAssessed")])

ns_param_asmnts_rolling = merge(ns_param_asmnts, totd, all = TRUE)

delist_abbrev = delistings[,c("ASSESS_ID","R3172ParameterName","delisting_notes")]
ns_303d_delistings = merge(ns_param_asmnts_rolling, delist_abbrev, all.x = TRUE)
ns_303d_delistings = subset(ns_303d_delistings, is.na(ns_303d_delistings$delisting_notes))
ns_303d_delistings$CycleFirstListed = ifelse(is.na(ns_303d_delistings$CycleFirstListed),"2020",ns_303d_delistings$CycleFirstListed)
ns_303d_delistings$param_DWQasmnt = "NS"
ns_303d_delistings$Parameter_EPACat_2020 = 5
ns_303d_delistings = ns_303d_delistings[,!names(ns_303d_delistings)%in%c("AU_NAME","Parameter_EPACat","delisting_notes")]

ns_303d_delistings = merge(ns_303d_delistings, au_auid_audesc, all.x = TRUE)
ns_303d_delistings = merge(ns_303d_delistings, au_wmu, all.x = TRUE)
ns_303d_delistings = merge(ns_303d_delistings, au_geom[,c("ASSESS_ID","au_stream_len_miles")], all.x = TRUE)

## Add HH criteria to impairments
benuse = c("1C","3A","3B","3C","3D")
benuse1 = paste0("HH",benuse)
hh_ns = data.frame(R3172ParameterName = c(rep("Arsenic",5),rep("Mercury",5)), BeneficialUse = c(benuse,benuse),HHBeneficialUse = c(benuse1, benuse1))

ns_303d_delistings = merge(ns_303d_delistings, hh_ns, all.x = TRUE)
ns_303d_delistings$BeneficialUse = as.character(ns_303d_delistings$BeneficialUse)
ns_303d_delistings$BeneficialUse = ifelse(!is.na(ns_303d_delistings$HHBeneficialUse),paste0(ns_303d_delistings$BeneficialUse,";", ns_303d_delistings$HHBeneficialUse), ns_303d_delistings$BeneficialUse)
ns_303d_delistings = ns_303d_delistings[,!names(ns_303d_delistings)%in%c("HHBeneficialUse")]

# Remove parameters from 303d covered in TMDL
tmdls_abbrev = unique(tmdls[,c("ASSESS_ID","R3172ParameterName","TMDL ID")])

ns_303d_tmdls = merge(ns_303d_delistings, tmdls_abbrev, all.x = TRUE)

## TRUE 303D
ns_303d = subset(ns_303d_tmdls, is.na(ns_303d_tmdls$`TMDL ID`))

ns_303dwide = ns_303d%>%pivot_wider(names_from = BeneficialUse, values_from = BeneficialUse)
ns_303dwide = ns_303dwide[,c(1:11,14,19,18,20,12,13,17,16,15)]
ns_303dwide = ns_303dwide%>%unite("Impaired_Uses",c("1C;HH1C","1C","2A","2B","3A","3B","3C","3D","4"),sep = ";",remove = TRUE, na.rm = TRUE)

## ADD historical impairments previously placed in wrong AU's for geofile error into correct AUs
add_303d = readxl::read_xlsx("delisting_historical_geofile_error_correct_aus.xlsx", sheet = "Sheet1")
ns_303dwide = plyr::rbind.fill(ns_303dwide, add_303d)

# Cat 5 AUs from 303d
cat5_aus = unique(ns_303dwide$ASSESS_ID)

## 4A
ns_4a = subset(ns_303d_tmdls, !is.na(ns_303d_tmdls$`TMDL ID`))

fa1 = merge(fa1, au_geom[,c("ASSESS_ID","au_stream_len_miles")], all.x = TRUE)
fa_del = merge(fa1, delist_abbrev, all.x = TRUE)#0 of these were delisted
rm(fa_del)

ns_4a = ns_4a[,!names(ns_4a)%in%c("CycleFirstListed","AU_NAME","AU_DESCRIP","Mgmt_Unit","au_stream_len_miles_perrenial")]
ns_4a = merge(ns_4a, fa1, all = TRUE)
ns_4a$param_DWQasmnt = "NS"
ns_4a$Parameter_EPACat_2020 = 5
ns_4a$CycleFirstListed = ifelse(is.na(ns_4a$CycleFirstListed),"2020",ns_4a$CycleFirstListed)
ns_4a = merge(ns_4a, au_auid_audesc, all.x = TRUE)
ns_4a = merge(ns_4a, au_wmu, all.x = TRUE)
ns_4a = merge(ns_4a, au_geom[,c("ASSESS_ID","au_stream_len_miles")], all.x = TRUE)

ns_4awide = ns_4a%>%pivot_wider(names_from = BeneficialUse, values_from = BeneficialUse)
ns_4awide = ns_4awide[,c(1:11,16,17,18,13,12,19,15,14)]
ns_4awide = ns_4awide%>%unite("Impaired_Uses",c("1C","2A","2B","3A","3B","3C","3D","4"),sep = ";",remove = TRUE, na.rm = TRUE)
```

### 305b
For the 305b list, we need to discern between Fully Supporting and No Evidence of Impairment. We have programmed this functionality into our roll up function in the irTools package, but it requires some additional steps. In this section, we pulled all Fully Supporting AU's from the AU roll up, and then re-rolled up data from those AU's using the "expand uses" input in the R function. If a use contains an "NA" in the AssessCat category, this means that the AU has No Evidence of Impairment, but we did not assess all of its beneficial uses. These AU's are then re-connected to the rest of the assessments.

```{r}
# 305b
# Roll up to overall AU to find FS AU's
au_asmnts = irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME"), cat_var="IR_Cat", expand_uses=F, print=F)

fs_aus = subset(au_asmnts$ASSESS_ID, au_asmnts$AssessCat=="FS")
fs_prelim = subset(asmnts_no_pi, asmnts_no_pi$ASSESS_ID%in%fs_aus)

# Expand uses for FS cats to find cat 2's
fs_au_asmnts = irTools::rollUp(list(fs_prelim), group_vars=c("ASSESS_ID","AU_NAME","BeneficialUse"), cat_var="IR_Cat", expand_uses=T, print=F)

# Au's with NA's
nei_aus = subset(fs_au_asmnts, fs_au_asmnts$AssessCat=="NA"|fs_au_asmnts$AssessCat=="IDNE")
nei_auids = unique(nei_aus$ASSESS_ID)

names(au_asmnts)[names(au_asmnts)=="AssessCat"] = "AU_DWQasmnt"

# Add DWQ numeric category
au_asmnts = within(au_asmnts,{
  AU_EPACat_2020 = NA
  AU_EPACat_2020[AU_DWQasmnt=="NS"] = 5
  AU_EPACat_2020[AU_DWQasmnt=="IDEX"|AU_DWQasmnt=="IDNE"] = 3
  AU_EPACat_2020[AU_DWQasmnt=="FS"] = 1
})

# Add No Evidence of Impairment (Cat 2)
au_asmnts$AU_EPACat_2020 = ifelse(au_asmnts$ASSESS_ID%in%nei_auids, "2", au_asmnts$AU_EPACat_2020)

# Add Historic Assessments
au_asmnts_rolling = merge(au_asmnts, tofb, all = TRUE)
au_asmnts_rolling$IRCycleAULastAssessed = ifelse(is.na(au_asmnts_rolling$IRCycleAULastAssessed),"2020",au_asmnts_rolling$IRCycleAULastAssessed)
au_asmnts_rolling$IRCycleAULastAssessed = ifelse(!is.na(au_asmnts_rolling$AU_DWQasmnt),"2020",au_asmnts_rolling$IRCycleAULastAssessed)
au_asmnts_rolling$AU_EPACat_2020 = ifelse(is.na(au_asmnts_rolling$AU_EPACat_2020),au_asmnts_rolling$AU_EPACat,au_asmnts_rolling$AU_EPACat_2020)

# Add AU and WMU info
au_asmnts_rolling = au_asmnts_rolling[,!names(au_asmnts_rolling)%in%c("AU_NAME")]
au_asmnts_rolling = merge(au_asmnts_rolling, au_auid_audesc, all.x = TRUE)
au_asmnts_rolling = merge(au_asmnts_rolling, au_wmu, all.x = TRUE)
au_asmnts_rolling = merge(au_asmnts_rolling, au_geom[,c("ASSESS_ID","au_stream_len_miles")], all.x = TRUE)

# Add impaired TMDL listings
tmdl_aus = unique(ns_4awide$ASSESS_ID)
au_asmnts_rolling$AU_EPACat_2020 = ifelse(au_asmnts_rolling$ASSESS_ID%in%tmdl_aus, "4A",au_asmnts_rolling$AU_EPACat_2020)


# Incorporate 303d list AUs that are cat5
au_asmnts_rolling$AU_EPACat_2020 = ifelse(au_asmnts_rolling$ASSESS_ID%in%cat5_aus,"5",au_asmnts_rolling$AU_EPACat_2020)

# Change not-assessed cat 5s on delisting list to cat 3 because we have no assessments this cycle
ns_na_aus = subset(au_asmnts_rolling, au_asmnts_rolling$AU_EPACat_2020==5&is.na(au_asmnts_rolling$AU_DWQasmnt))
ns_na_aus_del = merge(ns_na_aus, delist_abbrev, all.x = TRUE)
ns_na_aus_del = subset(ns_na_aus_del, !is.na(ns_na_aus_del$R3172ParameterName)&!(ns_na_aus_del$ASSESS_ID=="UT14060009-004_02")) 
ns_na_aus1 = as.character(unique(ns_na_aus_del$ASSESS_ID))

au_asmnts_rolling$AU_EPACat_2020 = ifelse(au_asmnts_rolling$ASSESS_ID%in%ns_na_aus1, "3",au_asmnts_rolling$AU_EPACat_2020)

# Finalize columns
au_asmnts_rolling_1 = au_asmnts_rolling[,!names(au_asmnts_rolling)%in%c("AU_EPACat")]

```

```{r, echo = F}
# Writing the data to an excel file and a couple tests
write.csv(au_asmnts_rolling_1, "305b.csv", row.names = FALSE)
write.csv(ns_303dwide, "303d.csv", row.names = FALSE)
writexl::write_xlsx(list(
										`305b`=au_asmnts_rolling_1, 
										`303d`=ns_303dwide,
										`tmdls`=tmdls,
										`delistings`=delistings,
										`4A only`=ns_4awide
	), path=paste0('rivers_and_streams_file_v4.xlsx'), format_headers=F, col_names=T)

# ns_305b = as.character(au_asmnts_rolling_1$ASSESS_ID[au_asmnts_rolling_1$AU_EPACat_2020==5])
# ns_303d1 = as.character(unique(ns_303d$ASSESS_ID))
# orphs = ns_305b[!ns_305b%in%ns_303d1]
# 
# orph_d = subset(prelim_asmnts, prelim_asmnts$ASSESS_ID%in%orphs)
# orph_d = subset(prepped_data$acc_data, prepped_data$acc_data$ASSESS_ID%in%orphs)
# 
# test = merge(au_asmnts_rolling, delist_abbrev, all.x = TRUE)
# test = subset(test, !is.na(test$R3172ParameterName))
```

## Summary Stats
```{r}
## Total AUs
# totaus = subset(au_asmnts_rolling_1, !is.na(au_asmnts_rolling_1$AU_DWQasmnt))
# total_river_aus = length(unique(totaus$ASSESS_ID))
total_river_aus = length(unique(au_asmnts_rolling_1$ASSESS_ID))
## Total stream miles
# total_river_miles = sum(totaus$au_stream_len_miles)
aus_w_streammiles = subset(au_asmnts_rolling_1, !is.na(au_asmnts_rolling_1$au_stream_len_miles))
total_river_miles = sum(aus_w_streammiles$au_stream_len_miles)
## Total monitoring locations
total_monitoring_locations = length(unique(asmts_sr$IR_MLID))
## Number of assessed AU's in each category
cats_by_aucount = au_asmnts_rolling_1%>%group_by(AU_EPACat_2020)%>%summarise(AU_Count = length(ASSESS_ID))
## Stream miles in each category
cats_by_streammiles = aus_w_streammiles%>%group_by(AU_EPACat_2020)%>%summarise(Stream_Miles = sum(au_stream_len_miles))

# Breakdown by parameter
totd_fa = plyr::rbind.fill(ns_303dwide, ns_4awide)
totd_fa_4c = totd_fa[,c("ASSESS_ID","R3172ParameterName")]
c4 = data.frame("ASSESS_ID" = c("UT16030002-004_00","UT16020101-014_00"),"R3172ParameterName" = c("Habitat","Habitat"))

totd_fa_4c = plyr::rbind.fill(totd_fa_4c, c4)

params = unique(totd_fa_4c$R3172ParameterName)
groups = c("Metals","Metals","Inorganics","Metals","Metals","E. coli","E. coli","Physical","Metals","Metals","Macroinvertebrates","Physical","Physical","Inorganics","Physical","Metals","Inorganics","Inorganics","Metals","Pollution Indicator","Radiological","Habitat and Sedimentation","Radiological","Habitat and Sedimentation")
trans = data.frame(R3172ParameterName = params, ParameterGroup = groups)
totd_fa_4c = merge(totd_fa_4c, trans, all.x = TRUE)

ns_param_group_breakdowns = totd_fa_4c%>%group_by(ParameterGroup)%>%summarise(Impairment_Count = length(ASSESS_ID))

save(data_used, total_river_aus, total_river_miles, total_monitoring_locations, cats_by_aucount, cats_by_streammiles, ns_param_group_breakdowns, file = "execsum_stats_rivers_streams.RData")
```


## Compiled File
```{r}
compiled = unique(asmts_sr[,!names(asmts_sr)%in%c("AU_NAME","AU_DESCRIP","Mgmt_Unit","AU_Type","ASSESS_ID2016","Water_Type","R317Descrp","AU_NAME2016", "AU_DESCRIP.1","lake","pol_ind","confirmed_listing")])
compiled = merge(compiled, au_asmnts_rolling_1, all.x = TRUE)

# min and max dates
accd = prepped_data$acc_data
accd$ActivityStartDate = as.Date(as.character(accd$ActivityStartDate),"%Y-%m-%d")
prepd_min = accd%>%group_by(IR_MLID,R3172ParameterName)%>%summarize(min_date = min(ActivityStartDate))
prepd_max = accd%>%group_by(IR_MLID,R3172ParameterName)%>%summarize(max_date = max(ActivityStartDate))

prepd_por_dates = merge(prepd_min, prepd_max, all = TRUE)

snowbird_dat=as.data.frame(readxl::read_excel('P:/WQ/Integrated Report/IR_2020/2020-IR-assessments/assessment/99_external_assessments/snowbird/snowbird_asmnt.xlsx', 'assessed_data'))
snowbird_dat = unique(snowbird_dat[,c("MonitoringLocationIdentifier","Activity.Start.Date","R3172ParameterName")])
names(snowbird_dat) = c("IR_MLID","ActivityStartDate","R3172ParameterName")
snowbird_dat$R3172ParameterName[snowbird_dat$R3172ParameterName=="Temperature"] = "Max. Temperature"

sb_min = snowbird_dat%>%group_by(IR_MLID,R3172ParameterName)%>%summarize(min_date = min(ActivityStartDate))
sb_max = snowbird_dat%>%group_by(IR_MLID,R3172ParameterName)%>%summarize(max_date = max(ActivityStartDate))

sb_por_dates = merge(sb_min, sb_max, all = TRUE)

por_dates = plyr::rbind.fill(prepd_por_dates, sb_por_dates)

compiled = merge(compiled, por_dates, all.x = TRUE)


write.csv(compiled, "compiled_file_v1.csv", row.names = FALSE)
```


```{r}
## AU-Use roll up for ATTAINS
au_use_asmnts = irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME","BeneficialUse"), cat_var="IR_Cat", expand_uses=T, print=F)

# Combine overall cat and use cats
names(au_asmnts)[names(au_asmnts)=="AssessCat"] <- "DWQ_AU_Cat"
names(au_use_asmnts)[names(au_use_asmnts)=="AssessCat"] <- "DWQ_AU_Use_Cat"
au_use_cats = merge(au_use_asmnts, au_asmnts, all = TRUE)

# length(au_use_cats$DWQ_AU_Use_Cat[is.na(au_use_cats$DWQ_AU_Use_Cat)])
# length(au_use_cats$DWQ_AU_Cat[is.na(au_use_cats$DWQ_AU_Cat)])

# Add DWQ numeric category
au_use_cats = within(au_use_cats,{
  DWQ_AU_NumCat = NA
  DWQ_AU_NumCat[DWQ_AU_Cat=="NS"] = 5
  DWQ_AU_NumCat[DWQ_AU_Cat=="IDEX"|DWQ_AU_Cat=="IDNE"] = 3
  DWQ_AU_NumCat[DWQ_AU_Cat=="FS"] = 1
})

au_use_cats$DWQ_AU_NumCat = ifelse(au_use_cats$ASSESS_ID%in%nei_auids, "2", au_use_cats$DWQ_AU_NumCat)

rm(fs_aus, fs_prelim, fs_au_asmnts, nei_auids, nei_aus)

au_cats = unique(au_use_cats[,c("ASSESS_ID","DWQ_AU_Cat","DWQ_AU_NumCat")])
names(au_cats) = c("ASSESS_ID","AU_DWQCat_2020","AU_EPACat_2020")

au_cats_rolling = merge(au_cats, tofb, all = TRUE)
au_cats_rolling$ASSESS_ID = as.character(au_cats_rolling$ASSESS_ID)
```


### Combine AU cat and AU param cats, new and historic, for exercise/check
```{r, eval = FALSE}
library(tidyverse)
au_param_cats_rolling = merge(au_cats_rolling, ns_param_asmnts_rolling, all.x = TRUE)
au_param_cats_rolling$IRCycleAULastAssessed = ifelse(is.na(au_param_cats_rolling$AU_DWQCat_2020),au_param_cats_rolling$IRCycleAULastAssessed,"2020")

maxdat = prepped_data$acc_data
maxdat$ActivityStartDate = as.Date(as.character(maxdat$ActivityStartDate),"%Y-%m-%d")
max_date = maxdat%>%group_by(ASSESS_ID)%>%summarise(MaxDate = max(ActivityStartDate))
max_date$New_Data = ifelse(max_date$MaxDate>as.Date("2014-10-01"),"Y","N")

au_param_cats_rolling = merge(au_param_cats_rolling, max_date, all.x = TRUE)
write.csv(au_param_cats_rolling, "au_param_categories_historic_cats.csv", row.names = FALSE)
```

```{r, echo = F, eval = F}
# library(tidyr)
# library(dplyr)
# 
# load("tmdls_2020_ir.Rdata")
# tmdls = tmdls[,!names(tmdls)%in%c("Notes","SSC Definition","2018/2020 Prep: EFQuestion","JVL Comment/ Recommendation")]
# names(tmdls)[names(tmdls)=="Assessment Unit ID"] <- "ASSESS_ID"
# 
# tmdls_wide = tmdls%>%pivot_wider(id_cols = c(ASSESS_ID, `TMDL ID`), names_from = `TMDL Pollutant`, values_from = `TMDL Pollutant`)
# 
# paste2 <- function(x){
#   y = x[3:length(x)]
#   y = y[!is.na(y)]
#   z = paste(y, collapse=",")
#   return(z)
# }
# 
# tmdls_wide$Pollutant = apply(tmdls_wide,1,paste2)
# tmdls_wide = tmdls_wide[,c("ASSESS_ID","TMDL ID","Pollutant")]
# au_mgmt = unique(au_use_cats[,c("ASSESS_ID","AU_NAME","Mgmt_Unit")])
# tmdls_wide = merge(tmdls_wide, au_mgmt, all.x = TRUE)
# 
# b305 = merge(au_use_cats, tmdls_wide, all = TRUE)
# b305$DWQ_AU_NumCat = ifelse(!is.na(b305$`TMDL ID`)&(b305$DWQ_AU_Cat%in%c("NS","IDEX")),"4A",b305$DWQ_AU_NumCat)
# 
# b305_aulevel = unique(b305[,!names(b305)%in%c("BeneficialUse","DWQ_AU_Use_Cat")])

```


```{r, echo = F, eval= F}
# # Site assessments
# site_asmnts=irTools::rollUp(list(asmnts_no_pi), group_vars=c("IR_MLID","IR_MLNAME","ASSESS_ID","AU_NAME", "IR_Lat","IR_Long","Mgmt_Unit"), cat_var="IR_Cat", expand_uses=T, print=F)
# names(site_asmnts)[names(site_asmnts)=="AssessCat"]="site_asmnt"
# # names(site_asmnts)[names(site_asmnts)=="BeneficialUse"]="site_bu"
# 
# # AU assessments (no uses)
# au_asmnts=irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME"), cat_var="IR_Cat", expand_uses=T, print=F)
# names(au_asmnts)[names(au_asmnts)=="AssessCat"]="au_asmnt"
# # names(au_asmnts)[names(au_asmnts)=="BeneficialUse"]="au_bu"
# site_au_asmnts=merge(site_asmnts, au_asmnts, all=T)
# 
# # AU-site-param assessments
# param_asmnts= irTools::rollUp(list(asmnts_no_pi), group_vars=c("IR_MLID","IR_MLNAME","ASSESS_ID","AU_NAME","R3172ParameterName"), cat_var="IR_Cat", expand_uses=F, print=F)
# names(param_asmnts)[names(param_asmnts)=="AssessCat"]="param_asmnt"
# # names(param_asmnts)[names(param_asmnts)=="BeneficialUse"]="param_bu"
# 
# # Combine all assessments
# site_au_param_asmnts = merge(site_au_asmnts, param_asmnts, all = TRUE)
# write.csv(file="site_au_param_asmnts_merged.csv", site_au_param_asmnts, row.names=F)
# 
# ##### AU-site-use-param assessments
# au_use_asmnts=irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME","BeneficialUse"), cat_var="IR_Cat", expand_uses=T, print=F)
# names(au_asmnts)[names(au_asmnts)=="AssessCat"]="au_asmnt"
# site_au_use_param_asmnts= irTools::rollUp(list(asmnts_no_pi), group_vars=c("IR_MLID","IR_MLNAME","ASSESS_ID","AU_NAME","BeneficialUse","R3172ParameterName"), cat_var="IR_Cat", expand_uses=F, print=F)
# names(site_au_use_param_asmnts)[names(site_au_use_param_asmnts)=="AssessCat"]="param_asmnt"
# 
# au_use_site_param_asmts = merge(au_use_asmnts, site_au_use_param_asmnts, all = TRUE)
# write.csv(file="site_au_use_param_asmnts_merged.csv", au_use_site_param_asmts, row.names=F)
```

```{r, eval = F}
# Pollution Indicator Assessments
pi_asmnts = subset(prelim_asmnts, prelim_asmnts$ParameterGroupName=="POLLUTION INDICATORS")
pi_au_param_asmnts = irTools::rollUp(list(pi_asmnts), group_vars = c("ASSESS_ID","AU_NAME","R3172ParameterName"), cat_var = "AssessCat", expand_uses = F, print = F)
```

#### Add 2016 IR Cycle Last Assessed
Cycle last assessed comes from the legally binding IR tables from the DWQ website, while the cycle first listed comes from ATTAINS. The cycle last assessed does not occur on the use level, while the cycle first listed is tied to a parameter-use combination.
```{r, echo = F, eval = F}
# # Cycle last assessed - from IR website
# sixteen_cla = readxl::read_xlsx("cyc_last_assessed_first_listed.xlsx", sheet = "website_2016_305b")
# 
# au_use_cats = merge(au_use_cats, sixteen_cla, all= TRUE)
# au_use_cats$CycleLastAssessed = ifelse(is.na(au_use_cats$Mgmt_Unit),au_use_cats$IRCycleAULastAssessed,"2020")
```

#### Add Cycle First Listed 
```{r, echo = F, eval = F}
# Cycle first listed - from ATTAINS
sixteen_cfl = readxl::read_xlsx("cyc_last_assessed_first_listed.xlsx", sheet = "attains_303d")
attains_uses = readxl::read_xlsx("ATTAINS_domains.xlsx", sheet = "uses")

sixteen_cfl = merge(sixteen_cfl, attains_uses, all.x = TRUE)

attains_parms = readxl::read_xlsx("ATTAINS_domains.xlsx", sheet = "params")
names(attains_parms)[names(attains_parms)=="PARAM_NAME"] = "PARAMETER_CODE_NAME"
ns_param_asmnts = merge(ns_param_asmnts, attains_parms, all.x = TRUE)

ns_parms_cfl = merge(ns_param_asmnts, sixteen_cfl, all = TRUE)
ns_parms_cfl$FIRST_LISTED_CYCLE = ifelse(!is.na(ns_parms_cfl$Mgmt_Unit)&is.na(ns_parms_cfl$FIRST_LISTED_CYCLE),"2020",ns_parms_cfl$FIRST_LISTED_CYCLE)
write.csv(ns_parms_cfl, "303d_Test.csv", row.names = F)
```

#### Widen by AU
```{r, echo = F, eval = F}
ns_uses_wide = unique(ns_param_asmnts[,c("ASSESS_ID","AU_NAME","BeneficialUse")])
ns_uses_wide = ns_uses_wide[order(ns_uses_wide$BeneficialUse),]
ns_uses_wide = ns_uses_wide%>%pivot_wider(id_cols = c(ASSESS_ID, AU_NAME), names_from = BeneficialUse, values_from = BeneficialUse)

ns_uses_wide$Impaired_Uses = apply(ns_uses_wide,1,paste2)
ns_uses_wide = ns_uses_wide[,c("ASSESS_ID","AU_NAME","Impaired_Uses")]

ns_params_wide = unique(ns_param_asmnts[,c("ASSESS_ID","AU_NAME","R3172ParameterName")])
ns_params_wide = ns_params_wide%>%pivot_wider(id_cols = c(ASSESS_ID, AU_NAME), names_from = R3172ParameterName, values_from = R3172ParameterName)

ns_params_wide$Impaired_Parameter = apply(ns_params_wide,1,paste2)
ns_params_wide = ns_params_wide[,c("ASSESS_ID","AU_NAME","Impaired_Parameter")]

d303 = merge(ns_uses_wide, ns_params_wide, all= TRUE)
d303 = merge(d303, au_mgmt, all.x = TRUE)
```


#### Add Vision Priorities
```{r, echo = F, eval = F}
vision = read.csv("P:\\WQ\\Integrated Report\\IR_2020\\attains\\priorities\\UTAHDWQ_priorities_2016.csv")

names(vision) = c("ASSESS_ID","AU_NAME","ATTAINS_PARAM","Catchment_Size_sqmi")
params = unique(vision$ATTAINS_PARAM)
newparm_names = c("Cadmium","E. coli","Minimum Dissolved Oxygen","Zinc","Arsenic","Max. Temperature","Aluminum", "pH")
translation = data.frame(ATTAINS_PARAM = params, R3172ParameterName=newparm_names)

vision = merge(vision, translation, all = TRUE)
vision$EPA_Priority = "High"
vision = vision[,!names(vision)%in%"ATTAINS_PARAM"]

d303 = merge(d303, vision, all = TRUE)
```

#### New Listings

```{r, echo = F, eval = F}
### COMPARISON of 303d lists
current_listings=read.csv(file='current_listings.csv')
names(current_listings)[names(current_listings)=="PARAM_NAME"] = "PARAMETER_CODE_NAME"

overlap_twofiles = merge(current_listings, sixteen_cfl, all = TRUE)
write.csv(overlap_twofiles, "current_listings_twofiles.csv", row.names = FALSE)
```


```{r, echo = F, eval = F}
au_parm_rollup = irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME","Mgmt_Unit","R3172ParameterName"), cat_var="IR_Cat", expand_uses=F, print=F)

ns = subset(au_parm_rollup, au_parm_rollup$AssessCat=="NS")
ns$AU_EPACat_2020 = 5

new_ns = merge(ns, current_listings, all.x = TRUE)
new_ns = subset(new_ns, is.na(new_ns$AU_EPACat))

new_ns_tmdls = merge(new_ns, tmdls_wide, all.x = TRUE)

write.csv(new_ns_tmdls, "new_au_param_cat5_listings.csv", row.names = FALSE)
```

