# Roll up assessments to various levels {#rollup-asmnts}

## Add Delistings

```{r}

```

## Add Spatial Information, including AU Re-segmentation
```{r}
spatial = read.csv("P:\\WQ\\Integrated Report\\IR_2020\\2020-IR-assessments\\spatial_files\\au_geometry.csv")

site_au_reseg = readxl::read_xlsx("P:\\WQ\\Integrated Report\\IR_2020\\2020-IR-assessments\\spatial_files\\au_reseg\\site_au_reseg.xlsx", sheet = "Resgement sites")

mlid_au_res = unique(site_au_reseg[,c("IR_MLID","AUID2016","RESEG2020")])
mlid_au_res$ASSESS_ID = mlid_au_res$AUID2016

prelim_asmnts_res = merge(mlid_au_res, prelim_asmnts, all.x = TRUE)
prelim_asmnts_nores = subset(prelim_asmnts, !prelim_asmnts$ASSESS_ID%in%unique(mlid_au_res$ASSESS_ID))

dim(prelim_asmnts_res)[1]+dim(prelim_asmnts_nores)[1]==dim(prelim_asmnts)[1]
```


## Remove Pollution Indicators
Pollution indicators must be removed from roll up to ensure assessment units are assessed appropriately

```{r}
pi_recs = subset(prelim_asmnts, prelim_asmnts$ParameterGroupName=="POLLUTION INDICATORS")
pi_recs$pi = 1
asmnts_no_pi = merge(prelim_asmnts, pi_recs, all.x=TRUE)
asmnts_no_pi = subset(asmnts_no_pi, is.na(asmnts_no_pi$pi))
au_bu = unique(asmnts_no_pi[,c("BEN_CLASS","ASSESS_ID")])
au_bu = au_bu[!is.na(au_bu$BEN_CLASS),]
asmnts_no_pi = asmnts_no_pi[,!names(asmnts_no_pi)%in%c("BEN_CLASS")]
asmnts_no_pi = merge(asmnts_no_pi, au_bu, all.x = TRUE)
asmnts_no_pi = within(asmnts_no_pi,{
  AU_Type[AU_Type=="Lake / Reservoir"] = "Reservoir/Lake"
  AU_Type[AU_Type=="River / Stream"] = "River/Stream"
})
rm(pi_recs, au_bu)
```


## Generate merged site & AU assessments

```{r, eval= F}
# Site assessments
site_asmnts=irTools::rollUp(list(asmnts_no_pi), group_vars=c("IR_MLID","IR_MLNAME","ASSESS_ID","AU_NAME", "IR_Lat","IR_Long","Mgmt_Unit"), cat_var="IR_Cat", expand_uses=T, print=F)
names(site_asmnts)[names(site_asmnts)=="AssessCat"]="site_asmnt"
# names(site_asmnts)[names(site_asmnts)=="BeneficialUse"]="site_bu"

# AU assessments (no uses)
au_asmnts=irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME"), cat_var="IR_Cat", expand_uses=T, print=F)
names(au_asmnts)[names(au_asmnts)=="AssessCat"]="au_asmnt"
# names(au_asmnts)[names(au_asmnts)=="BeneficialUse"]="au_bu"
site_au_asmnts=merge(site_asmnts, au_asmnts, all=T)

# AU-site-param assessments
param_asmnts= irTools::rollUp(list(asmnts_no_pi), group_vars=c("IR_MLID","IR_MLNAME","ASSESS_ID","AU_NAME","R3172ParameterName"), cat_var="IR_Cat", expand_uses=F, print=F)
names(param_asmnts)[names(param_asmnts)=="AssessCat"]="param_asmnt"
# names(param_asmnts)[names(param_asmnts)=="BeneficialUse"]="param_bu"

# Combine all assessments
site_au_param_asmnts = merge(site_au_asmnts, param_asmnts, all = TRUE)
write.csv(file="site_au_param_asmnts_merged.csv", site_au_param_asmnts, row.names=F)

##### AU-site-use-param assessments
au_use_asmnts=irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME","BeneficialUse"), cat_var="IR_Cat", expand_uses=T, print=F)
names(au_asmnts)[names(au_asmnts)=="AssessCat"]="au_asmnt"
site_au_use_param_asmnts= irTools::rollUp(list(asmnts_no_pi), group_vars=c("IR_MLID","IR_MLNAME","ASSESS_ID","AU_NAME","BeneficialUse","R3172ParameterName"), cat_var="IR_Cat", expand_uses=F, print=F)
names(site_au_use_param_asmnts)[names(site_au_use_param_asmnts)=="AssessCat"]="param_asmnt"

au_use_site_param_asmts = merge(au_use_asmnts, site_au_use_param_asmnts, all = TRUE)
write.csv(file="site_au_use_param_asmnts_merged.csv", au_use_site_param_asmts, row.names=F)
```

```{r, eval = F}
# Pollution Indicator Assessments
pi_asmnts = subset(prelim_asmnts, prelim_asmnts$ParameterGroupName=="POLLUTION INDICATORS")
pi_au_param_asmnts = irTools::rollUp(list(pi_asmnts), group_vars = c("ASSESS_ID","AU_NAME","R3172ParameterName"), cat_var = "AssessCat", expand_uses = F, print = F)
```

## Generate 305b and 303d lists

### 305b
For the 305b list, we need to discern between Fully Supporting and No Evidence of Impairment. We have programmed this functionality into our roll up function in the irTools package, but it requires some additional steps. In this section, we pulled all Fully Supporting AU's from the AU roll up, and then re-rolled up data from those AU's using the "expand uses" input in the R function. If a use contains an "NA" in the AssessCat category, this means that the AU has No Evidence of Impairment, but we did not assess all of its beneficial uses. These AU's are then re-connected to the rest of the assessments.
```{r, 305b}
# Roll up to overall AU to find FS AU's
au_asmnts = irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME","BEN_CLASS","AU_Type","Mgmt_Unit"), cat_var="IR_Cat", expand_uses=F, print=F)

fs_aus = subset(au_asmnts$ASSESS_ID, au_asmnts$AssessCat=="FS")
fs_prelim = subset(asmnts_no_pi, asmnts_no_pi$ASSESS_ID%in%fs_aus)

# Expand uses for FS cats to find cat 2's
fs_au_asmnts = irTools::rollUp(list(fs_prelim), group_vars=c("ASSESS_ID","AU_NAME","BeneficialUse"), cat_var="IR_Cat", expand_uses=T, print=F)

# Au's with NA's
nei_aus = subset(fs_au_asmnts, fs_au_asmnts$AssessCat=="NA"|fs_au_asmnts$AssessCat=="IDNE")
nei_auids = unique(nei_aus$ASSESS_ID)

au_use_asmnts = irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME","BeneficialUse"), cat_var="IR_Cat", expand_uses=T, print=F)

# Combine overall cat and use cats
names(au_asmnts)[names(au_asmnts)=="AssessCat"] <- "DWQ_AU_Cat"
names(au_use_asmnts)[names(au_use_asmnts)=="AssessCat"] <- "DWQ_AU_Use_Cat"
au_use_cats = merge(au_use_asmnts, au_asmnts, all = TRUE)

# length(au_use_cats$DWQ_AU_Use_Cat[is.na(au_use_cats$DWQ_AU_Use_Cat)])
# length(au_use_cats$DWQ_AU_Cat[is.na(au_use_cats$DWQ_AU_Cat)])

# Add DWQ numeric category
au_use_cats = within(au_use_cats,{
  DWQ_AU_NumCat = NA
  DWQ_AU_NumCat[DWQ_AU_Cat=="NS"] = 5
  DWQ_AU_NumCat[DWQ_AU_Cat=="IDEX"|DWQ_AU_Cat=="IDNE"] = 3
  DWQ_AU_NumCat[DWQ_AU_Cat=="FS"] = 1
})

au_use_cats$DWQ_AU_NumCat = ifelse(au_use_cats$ASSESS_ID%in%nei_auids, "2", au_use_cats$DWQ_AU_NumCat)

rm(fs_aus, fs_prelim, fs_au_asmnts, nei_auids, nei_aus)
```

#### Add 2016 IR Cycle Last Assessed
Cycle last assessed comes from the legally binding IR tables from the DWQ website, while the cycle first listed comes from ATTAINS. The cycle last assessed does not occur on the use level, while the cycle first listed is tied to a parameter-use combination.
```{r, cycle}
# Cycle last assessed - from IR website
sixteen_cla = readxl::read_xlsx("cyc_last_assessed_first_listed.xlsx", sheet = "website_2016_305b")

au_use_cats = merge(au_use_cats, sixteen_cla, all= TRUE)
au_use_cats$CycleLastAssessed = ifelse(is.na(au_use_cats$Mgmt_Unit),au_use_cats$IRCycleAULastAssessed,"2020")
```

#### Add TMDLs to roll up
TMDL data from the following file:
"P:\WQ\Integrated Report\IR_2020\approved_tmdls\Approved_TMDLs_08122019_v3.xlsx"
```{r, tmdls}
library(tidyr)
library(dplyr)

load("tmdls_2020_ir.Rdata")
tmdls = unique(tmdls[,c("Assessment Unit ID","TMDL ID","TMDL Pollutant")])
names(tmdls)[names(tmdls)=="Assessment Unit ID"] <- "ASSESS_ID"

tmdls_wide = tmdls%>%pivot_wider(id_cols = c(ASSESS_ID, `TMDL ID`), names_from = `TMDL Pollutant`, values_from = `TMDL Pollutant`)

paste2 <- function(x){
  y = x[3:length(x)]
  y = y[!is.na(y)]
  z = paste(y, collapse=",")
  return(z)
}

tmdls_wide$Pollutant = apply(tmdls_wide,1,paste2)
tmdls_wide = tmdls_wide[,c("ASSESS_ID","TMDL ID","Pollutant")]
au_mgmt = unique(au_use_cats[,c("ASSESS_ID","AU_NAME","Mgmt_Unit")])
tmdls_wide = merge(tmdls_wide, au_mgmt, all.x = TRUE)

b305 = merge(au_use_cats, tmdls_wide, all = TRUE)
b305$DWQ_AU_NumCat = ifelse(!is.na(b305$`TMDL ID`)&(b305$DWQ_AU_Cat%in%c("NS","IDEX")),"4A",b305$DWQ_AU_NumCat)

b305_aulevel = unique(b305[,!names(b305)%in%c("BeneficialUse","DWQ_AU_Use_Cat")])

```

### 303(d) List
```{r}
ns_param_asmnts = irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME","BeneficialUse", "Mgmt_Unit","R3172ParameterName"), cat_var="IR_Cat", expand_uses=F, print=F)
au_mgmt = unique(ns_param_asmnts[,c("ASSESS_ID","Mgmt_Unit")])

ns_param_asmnts = subset(ns_param_asmnts, ns_param_asmnts$AssessCat=="NS")

#### Add HHC to 303d
hhc_ns = subset(prelim_asmnts, prelim_asmnts$TableDescription=="LIST OF HUMAN HEALTH CRITERIA (CONSUMPTION)"&prelim_asmnts$IR_Cat=="NS")
hhc_ns = unique(hhc_ns[,c("ASSESS_ID","AU_NAME","BeneficialUse","Mgmt_Unit","R3172ParameterName")])
hhc_ns$BeneficialUse = paste0("HH",hhc_ns$BeneficialUse)
hhc_ns$AssessCat = "NS"

# Flattened by use and parameter
ns_param_asmnts = plyr::rbind.fill(ns_param_asmnts, hhc_ns)
```

#### Add Cycle First Listed 
```{r}
# Cycle first listed - from ATTAINS
sixteen_cfl = readxl::read_xlsx("cyc_last_assessed_first_listed.xlsx", sheet = "attains_303d")
attains_uses = readxl::read_xlsx("ATTAINS_domains.xlsx", sheet = "uses")

sixteen_cfl = merge(sixteen_cfl, attains_uses, all.x = TRUE)

attains_parms = readxl::read_xlsx("ATTAINS_domains.xlsx", sheet = "params")
names(attains_parms)[names(attains_parms)=="PARAM_NAME"] = "PARAMETER_CODE_NAME"
ns_param_asmnts = merge(ns_param_asmnts, attains_parms, all.x = TRUE)

ns_parms_cfl = merge(ns_param_asmnts, sixteen_cfl, all = TRUE)
ns_parms_cfl$FIRST_LISTED_CYCLE = ifelse(!is.na(ns_parms_cfl$Mgmt_Unit)&is.na(ns_parms_cfl$FIRST_LISTED_CYCLE),"2020",ns_parms_cfl$FIRST_LISTED_CYCLE)
write.csv(ns_parms_cfl, "303d_Test.csv", row.names = F)
```

#### Widen by AU
```{r}
ns_uses_wide = unique(ns_param_asmnts[,c("ASSESS_ID","AU_NAME","BeneficialUse")])
ns_uses_wide = ns_uses_wide[order(ns_uses_wide$BeneficialUse),]
ns_uses_wide = ns_uses_wide%>%pivot_wider(id_cols = c(ASSESS_ID, AU_NAME), names_from = BeneficialUse, values_from = BeneficialUse)

ns_uses_wide$Impaired_Uses = apply(ns_uses_wide,1,paste2)
ns_uses_wide = ns_uses_wide[,c("ASSESS_ID","AU_NAME","Impaired_Uses")]

ns_params_wide = unique(ns_param_asmnts[,c("ASSESS_ID","AU_NAME","R3172ParameterName")])
ns_params_wide = ns_params_wide%>%pivot_wider(id_cols = c(ASSESS_ID, AU_NAME), names_from = R3172ParameterName, values_from = R3172ParameterName)

ns_params_wide$Impaired_Parameter = apply(ns_params_wide,1,paste2)
ns_params_wide = ns_params_wide[,c("ASSESS_ID","AU_NAME","Impaired_Parameter")]

d303 = merge(ns_uses_wide, ns_params_wide, all= TRUE)
d303 = merge(d303, au_mgmt, all.x = TRUE)
```


#### Add Vision Priorities
```{r, vision}
vision = read.csv("P:\\WQ\\Integrated Report\\IR_2020\\attains\\priorities\\UTAHDWQ_priorities_2016.csv")

names(vision) = c("ASSESS_ID","AU_NAME","ATTAINS_PARAM","Catchment_Size_sqmi")
params = unique(vision$ATTAINS_PARAM)
newparm_names = c("Cadmium","E. coli","Minimum Dissolved Oxygen","Zinc","Arsenic","Max. Temperature","Aluminum", "pH")
translation = data.frame(ATTAINS_PARAM = params, R3172ParameterName=newparm_names)

vision = merge(vision, translation, all = TRUE)
vision$EPA_Priority = "High"
vision = vision[,!names(vision)%in%"ATTAINS_PARAM"]

d303 = merge(d303, vision, all = TRUE)
```

#### New Listings

```{r}
### COMPARISON of 303d lists
current_listings=read.csv(file='current_listings.csv')
names(current_listings)[names(current_listings)=="PARAM_NAME"] = "PARAMETER_CODE_NAME"

overlap_twofiles = merge(current_listings, sixteen_cfl, all = TRUE)
write.csv(overlap_twofiles, "current_listings_twofiles.csv", row.names = FALSE)
```


```{r}
au_parm_rollup = irTools::rollUp(list(asmnts_no_pi), group_vars=c("ASSESS_ID","AU_NAME","Mgmt_Unit","R3172ParameterName"), cat_var="IR_Cat", expand_uses=F, print=F)

ns = subset(au_parm_rollup, au_parm_rollup$AssessCat=="NS")
ns$AU_EPACat_2020 = 5

new_ns = merge(ns, current_listings, all.x = TRUE)
new_ns = subset(new_ns, is.na(new_ns$AU_EPACat))

new_ns_tmdls = merge(new_ns, tmdls_wide, all.x = TRUE)

write.csv(new_ns_tmdls, "new_au_param_cat5_listings.csv", row.names = FALSE)
```

```{r}
writexl::write_xlsx(list("305b" = b305,"303d" = d303, "4as" = tmdls_wide),
		path = '305b_303d_tmdls_v2.xlsx', format_headers=F, col_names=T)
```

